Bird beak's elaboration and exploration

### 2022-04-21 Analysis/02-mcmcmcglmmm_analysis.Rmd
Update 02-mcmcmcglmmm_analysis.Rmd

```{r, parametrise_the_model, eval = FALSE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = shapespace,
                                   dimensions   = selected_dim,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "level1", "level2"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 100000,
                                       thin   = 500,
                                       burnin = 0))

>>>>

```{r, parametrise_the_model, eval = FALSE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = shapespace,
                                   dimensions   = selected_dim,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "level1", "level2"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 50000,
                                       thin   = 500,
                                       burnin = 0))
